### 2025-04-20 paper-reviews/papers-2025.tex
Add Intel hides behind ICC paper
Add effective attention paper

    The paper describes how Rotary Position Embedding (RoPE) is used by Transformer models to discern positional information in the input sequence. The authors studied extrapolation capabilities of Large Language Models based on RoPE with focus on modifications to rotary base. The paper proposed "Scaling Laws of RoPE-based Extrapolation", a framework to describe relations between the extrapolation performance and rotary base values as well as tunning context length.
\end{itemize}

@@

    The article highlights optimization challenges that database developers face while working on big data analysis. The author demonstrates performance drawbacks of reading large databases for different kind of analyses. The article is largely focused on efficient usage of hardware capabilities: random vs. sequential access to storage devices. There is a good diagram that compares random and sequential accesses of hard drives, SSDs and DRAM. The author also shows few possible database architecture focusing on possible read requests that are supposed to be serviced by the database. There is also a good definition of "big data" in the very end of the paper.
\end{itemize}

>>>>

    The paper describes how Rotary Position Embedding (RoPE) is used by Transformer models to discern positional information in the input sequence. The authors studied extrapolation capabilities of Large Language Models based on RoPE with focus on modifications to rotary base. The paper proposed "Scaling Laws of RoPE-based Extrapolation", a framework to describe relations between the extrapolation performance and rotary base values as well as tunning context length.

    \item \cite{Luong:AttentionNMT:2015}:

    The authors present earlier attention-based models for machine translation tasks. The paper considers global and local attention approaches. The global approach attends to all words in the input sequence while the local one only looks at a subset of input words at a time. The article proposes and compares several mechanisms to decide what words in input sequence to attend to for the local attention approach. The resulting model yields a new state-of-the-art result in English to German translation task.
\end{itemize}

@@

    The article highlights optimization challenges that database developers face while working on big data analysis. The author demonstrates performance drawbacks of reading large databases for different kind of analyses. The article is largely focused on efficient usage of hardware capabilities: random vs. sequential access to storage devices. There is a good diagram that compares random and sequential accesses of hard drives, SSDs and DRAM. The author also shows few possible database architecture focusing on possible read requests that are supposed to be serviced by the database. There is also a good definition of "big data" in the very end of the paper.

    \item \cite{Gwennap:IntelHidesBehindICC:2017}:

    The article highlights how Intel uses ICC compiler and library optimizations to submit higher SPEC CPU scores. The author emphasizes that it is important to use GCC --- an open sources, harder to manipulate compiler --- to achieve apple to apple comparison of different vendors' processors.
\end{itemize}
